EU-Circle Case study 5

### 2016-11-29 EU-Circle/eu-circle_case-study-1.Rmd
EU-Circle new analysis

---
title: "eu-circle_case-study-1"
author: "Rasmus Benestad"
date: "May 2, 2016"
output: html_document
bibliography: bibliography.bib
---

@@

```{r,warning=FALSE}
amncd <- annual(ncd)
plot(amncd,col=c(rgb(0,0,1),rgb(1,0.3,0)),new=FALSE)
grid()
lines(trend(subset(amncd,is=1)),lty=2)
mcdd <- trend(subset(amncd,is=2))
lines(mcdd,lty=1)
print(attr(mcdd,'coefficients'))
```

@@

```{r,warning=FALSE}
X <- retrieve('data.ECAD/rr_0.25deg_reg_v12.0.nc',lon=c(4,8),lat=c(43,46))
map(X,new=FALSE)
```

>>>>

---
title: "eu-circle_case-study-1"
author: "Rasmus Benestad"
date: "May 2, 2016"
output:
  pdf_document: default
  html_document: default
bibliography: bibliography.bib
---

@@

```{r,warning=FALSE}
amncd <- annual(ncd)
plot(amncd,col=c(rgb(0,0,1),rgb(1,0.3,0)),new=FALSE,map.show=FALSE)
grid()
lines(trend(subset(amncd,is=1)),lty=2)
mcdd <- trend(subset(amncd,is=2))
lines(mcdd,lty=1)
print(attr(mcdd,'coefficients'))
```

@@

```{r,warning=FALSE}
X <- retrieve('data.ECAD/rr_0.25deg_reg.nc',lon=c(4,8),lat=c(43,46))
map(X,new=FALSE)
```

### 2016-11-29 EU-Circle/eu-circle_case-study-5.Rmd
Added a set with new Rmd scripts
EU-Circle new analysis

---
title: "EU-Circle Case study 5"
author: "Rasmus Benestad"
date: "May 2, 2016"
output: html_document
---

@@

>>>>

---
title: "EU-Circle Case study 5"
author: "Rasmus Benestad"
date: "May 2, 2016"
output:
  pdf_document: default
  html_document: default
---

@@

## Analysis: precipitation

Data from ECA&D: precipitation. Snow depth?

```{r}
library(esd)
ss <- select.station(param='precip',cntr='Germany',alt=250,nmin=75)
map(ss,new=FALSE)
Y <- subset(station(ss),it=c(1950,2015))
diagnose(Y)
```

Area total precipitation from gridded EOBS.

```{r}
rr <- retrieve('data.ECAD/rr_0.25deg_reg.nc',lon=c(5,15),lat=c(45,55))
map(rr,new=FALSE)
Arr <- aggregate.area(rr)
plot(rr,new=FALSE)
```

## Analysis: temperature

```{r}
library(esd)
ss <- select.station(param='temperature',cntr='Germany',alt=500,nmin=75)
map(ss)
X <- subset(station(ss),it='mam')
diagnose(X)
```
